An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-10 EconGrowth.Rnw
Added new to-do item for variables for fighre height and width where not already implemented.
Now including a graph of single-factor models in the paper.

\section*{To-do List}
\begin{itemize}
\item Reese: Add text from Word verson of paper to the LaTeX version.
\item Heun: Deal with missing covariance numbers when columns have unequal length.
\item Heun: Add $k$, $l$, $q$, $x$, and $u$ ONLY fits
\item Heun: Add CES production function fits
\item Heun: Add Linex production function fits
\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email but have not heard a response.
      \begin{itemize}
      \item ZA: lower bound on $\lambda$ and upper bound on $\alpha$
      \item ZM: lower bound on $\lambda$
      \end{itemize}
\item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
\item \st{Heun: Create a table of AIC values for each fit.}
\item \st{Heun: Add $u$ predictions for Cobb-Douglas}
\item \st{Heun: move tables to an appendix at the end.}
\item \st{Heun: Add acknowledgements (Dad, Pruim)}
\item \st{Heun: Add $u$ parameter table and graph}
\item \st{Heun: Add covariance metrics.}
\end{itemize}

@@

<<setup, echo=FALSE, message=FALSE>>=
require(knitr)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(tikzDevice) #See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=FALSE)
opts_chunk$set(
  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
  tidy=FALSE,
  comment=NA,
  eval=TRUE,
  warning=FALSE, #Tells whether to show warnings.
  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (cache=TRUE).
  cache=FALSE,
  echo=FALSE,    #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
  message=FALSE) #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.

@@

@@

Figure \ref{fig:Factors_Lattice_Graph} shows historical data. GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$) track each other closely. Covariances among these variables are rather high as shown in Tables \ref{tab:iance_US} through \ref{tab:Covariance_ZM}.

<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.pos="H", fig.cap="The facts. Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
createFactorsLatticeGraph <- function(){
  dataTable <- loadData("All")
  graphType <- "b" #b is for both line and symbol
  lineTypes <- c(0, 1, 5, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
  colors <- c("black", "black", "black", "red", "blue", "darkorange") #line and symbol colors
  symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
  graph <- xyplot(iGDP+iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                  type = graphType,
                  index.cond = list(countryOrderForGraphs), #orders the panels.
                  layout = layoutSpec, 
                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
                  as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
                  pch = symbols, col.symbol = colors, #Controls symbol parameters
                  key=list(text=list(c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")),
                           type=graphType,
                           cex=keyTextSize, #controls size of text in the key
                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
                           pch=symbols, col=colors, #controls symbol (plot characters) types
                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
                  scales=list(cex=scaleTextSize, #controls text size on scales.
                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                              y=list(relation="free", #allows each axis to be different
                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
                                     )
                              ),
                  ylim=list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)), #y axis limits
                  xlab="", ylab="Indexed (1980=1 or 1991=1)") #axis labels
  return(graph)
}
createFactorsLatticeGraph()
@

@@

<<single-factor functions, eval=TRUE>>=

@@

@@

<<cobb-douglas functions, eval=TRUE>>=
####################
# Returns an nls Cobb-Douglas model for the country specified
# Give an energyType ("Q", "X", or "U") if you want to include an energy term
##
cobbDouglasModel <- function(countryAbbrev, energyType){
  dataTable <- loadData(countryAbbrev) #Load the data that we need.
  #Run the non-linear least squares fit to the data based on whether we have an energy type or not.
  if (missing(energyType)){
    # No energy term desired in the Cobb-Douglas equation.
    # Establish guess values for alpha and lambda.
    lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
    alphaGuess <- 0.7 #0.7 gives good results for all countries.  
    # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
    modelCD <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha), 
                   data=dataTable, 
                   start = list(lambda=lambdaGuess, alpha=alphaGuess),
                   #Include the next 3 lines to fit with constraints.
                   #algorithm = "port",
                   #lower = list(lambda=-Inf, alpha=0), #constraints on lambda and alpha
                   #upper = list(lambda=Inf, alpha=1)
                   )
    return(modelCD)
  } else {
    # We need to do the Cobb-Douglas fit with the desired energy data.
    # To achieve the correct fit, we'll change the name of the desired column
    # to "iEToFit" and use "iEToFit" in the nls function. 
    energyColumnName <- paste("i", energyType, sep="") #Energy term desired in the Cobb-Douglas equation.
    eColIndex <- which(names(dataTable) %in% energyColumnName) #Find index of desired column
    colnames(dataTable)[eColIndex] <- "iEToFit" #Change desired column name to "iEToFit"
    # Reparameterize to ensure that we meet the constraints:
    # * alpha + beta + gamma = 1.0.
    # * alpha, beta, and gamma are all between 0.0 and 1.0.
    # To do this, we reparameterize as
    # * 0 < a < 1
    # * 0 < b < 1
    # * alpha = min(a, b)
    # * beta = b - a
    # * gamma = 1 - max(a, b)
    # Establish guess values for lambda, alpha, and beta.
    lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
    alphaGuess <- 0.9
    betaGuess <- 1.0 - alphaGuess
    aGuess <- alphaGuess
    bGuess <- alphaGuess + betaGuess
    # Now actually do the fit, using the column name "iEToFit".
    modelCDe <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEToFit^(1.0 - max(a,b)), 
                    data = dataTable,
                    start = list(lambda=lambdaGuess, a=aGuess, b=bGuess),
                    control = nls.control(maxiter = 200, 
                                          tol = 1e-05, 
                                          minFactor = 1/1024, 
                                          printEval=FALSE, #Tells whether to print details of curve fit process.
                                          warnOnly=TRUE),
                    #Include the next 3 lines to fit with constraints.
                    #algorithm = "port",
                    #lower = list(lambda=-Inf, a=0, b=0),
                    #upper = list(lambda= Inf, a=1, b=1)
                    )
    return(modelCDe)
  }
}

@@

#####################
# This function adds NA rows to a data.frame to ensure that the df is the same length as the country data set
##
padRows <- function(countryAbbrev, df){
  nRowsData <- nrow(loadData(countryAbbrev)) #Gets number of rows in data set
  nRowsDF <- nrow(df)
  nRowsToAdd <- nRowsData - nRowsDF
  nCol <- ncol(df)
  dfToAppend <- as.data.frame(matrix(NA, ncol=nCol, nrow=nRowsToAdd))
  colnames(dfToAppend) <- colnames(df)
  return(rbind(df, dfToAppend))
}

>>>>

\section*{To-do List}
\begin{itemize}
\item Reese: Add text from Word verson of paper to the LaTeX version.
\item Heun: Add setup variables for figure height and width where not already included.
\item Heun: Deal with missing covariance numbers when columns have unequal length.
\item Heun: Add $k$, $l$, $q$, $x$, and $u$ ONLY fits
\item Heun: Add CES production function fits
\item Heun: Add Linex production function fits
\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email but have not heard a response.
      \begin{itemize}
      \item ZA: lower bound on $\lambda$ and upper bound on $\alpha$
      \item ZM: lower bound on $\lambda$
      \end{itemize}
\item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
\item \st{Heun: Create a table of AIC values for each fit.}
\item \st{Heun: Add $u$ predictions for Cobb-Douglas}
\item \st{Heun: move tables to an appendix at the end.}
\item \st{Heun: Add acknowledgements (Dad, Pruim)}
\item \st{Heun: Add $u$ parameter table and graph}
\item \st{Heun: Add covariance metrics.}
\end{itemize}

@@

<<setup, echo=FALSE, message=FALSE>>=
require(knitr)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(tikzDevice) #See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=FALSE)
opts_chunk$set(
  # ********************************************************************************************************
  eval=TRUE,
  # ********************************************************************************************************
  warning=FALSE, #Tells whether to show warnings.
  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
  tidy=FALSE,
  comment=NA,
  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (cache=TRUE).
  cache=FALSE,
  echo=FALSE,    #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
  message=FALSE) #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.

@@

#####################
# This function adds NA rows to the end of a data.frame to ensure that the df is 
# the same length as the country data set
# returns a modified version of df that includes the padded rows filled with "NA".
##
padRows <- function(countryAbbrev, df){
  nRowsData <- nrow(loadData(countryAbbrev)) #Gets number of rows in data set
  nRowsDF <- nrow(df)
  nRowsToAdd <- nRowsData - nRowsDF
  nCol <- ncol(df)
  dfToAppend <- as.data.frame(matrix(NA, ncol=nCol, nrow=nRowsToAdd))
  colnames(dfToAppend) <- colnames(df)
  return(rbind(df, dfToAppend))
}

##############################
# Returns an integer representing the column index for some data
# dataTable the data.frame in which you want to change column names
# factor should be a string and one of Year, Y, K, L, Q, X, or U
##
columnIndex <- function(dataTable, factor){
  if (factor == "Year"){
    colName <- "iYear"
  } else if (factor == "Y"){
    colName <- "iGDP"
  } else if (factor == "K"){
    colName <- "iCapStk"
  } else if (factor == "L"){
    colName <- "iLabor"
  } else if (factor == "Q"){
    colName <- "iQ"
  } else if (factor == "X"){
    colName <- "iX"
  } else if (factor == "U"){
    colName <- "iU"
  } else {
    print(paste("Unknown factor:", factor, "in colIndex. Terminating execution."))
    quit()
  }
  # Get the desired column index.
  colIndex <- which(names(dataTable) %in% colName) #Find index of desired column
  return(colIndex)  
}

##############################
# Replaces a column name with the given string
# dataTable the data.frame that you're working with
# factor should be a string and one of Year, Y, K, L, Q, X, or U
# newName should be a string and the desired new name of the column
# returns dataTable with a new name for one of its factor column.
##
replaceColName <- function(dataTable, factor, newName){
  colIndex <- columnIndex(dataTable, factor)
  colnames(dataTable)[colIndex] <- newName #Change desired column name to newName
  return(dataTable)
}

@@

Figure \ref{fig:Factors_Lattice_Graph} shows historical data, including GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$). Facotrs of production track each other closely, and large covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.

<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.pos="H", fig.cap="Historical data. Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
createFactorsLatticeGraph <- function(){
  dataTable <- loadData("All")
  graphType <- "b" #b is for both line and symbol
  lineTypes <- c(0, 1, 5, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
  colors <- c("black", "black", "black", "red", "blue", "darkorange") #line and symbol colors
  symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
  graph <- xyplot(iGDP+iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                  type = graphType,
                  index.cond = list(countryOrderForGraphs), #orders the panels.
                  layout = layoutSpec, 
                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
                  as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
                  pch = symbols, col.symbol = colors, #Controls symbol parameters
                  key=list(text=list(c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")),
                           type=graphType,
                           cex=keyTextSize, #controls size of text in the key
                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
                           pch=symbols, col=colors, #controls symbol (plot characters) types
                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
                  scales=list(cex=scaleTextSize, #controls text size on scales.
                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                              y=list(relation="free", #allows each axis to be different
                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
                                     )
                              ),
                  ylim=list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)), #y axis limits
                  xlab="", ylab="Indexed (1980=1 or 1991=1)") #axis labels
  return(graph)
}
createFactorsLatticeGraph()
@

@@

<<single-factor functions, eval=TRUE>>=
####################
# Returns an nls single-factor model for the country and factor specified.
# factor should be one of "K", "L", "Q", "X", or "U".
##
singleFactorModel <- function(countryAbbrev, factor){
  dataTable <- loadData(countryAbbrev) #Load the data that we need.
  # We'll change the name of the desired column to "f"
  dataTable <- replaceColName(dataTable, factor, "f")
  # Now do the fit.
  lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
  mGuess <- 0.5
  # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
  modelSF <- nls(iGDP ~ exp(lambda*iYear) * f^m, 
                 data=dataTable, 
                 start = list(lambda=lambdaGuess, m=mGuess)
                 )
  return(modelSF)
}

#########################
# Takes the single-factor fitted models and creates per-country predictions for them.
# Returns a data.frame with the predictions.
##
singleFactorPredictions <- function(countryAbbrev, factor){
  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
  if (factor == "U"){
    if (!(haveData(countryAbbrev, factor))){
      #If we don't have data for this combination of countryAbbrev and energyType, 
      # return a column of NAs if the above conditions have been met.
      nRows <- 21 # All of these countries need 21 rows.
      df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
      colnames(df) <- "pred"
      return(df)
    }
  }
  model <- singleFactorModel(countryAbbrev, factor)
  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
  df <- data.frame(pred)
  # Pad with rows as necessary
  df <- padRows(countryAbbrev, df)
  return(df)
}

#########################
# Takes the single-factor fitted models and creates a single column of predicted GDP values
# that corresponds, row for row, with the AllData.txt file.
##
singleFactorPredictionsColumn <- function(factor){
  out <- do.call("rbind", lapply(countryAbbrevs, singleFactorPredictions, factor=factor))
  colnames(out) <- c(paste("predGDP", factor, sep=""))
  return(out)
}

##############################
# Creates a graph that plots predicted GDP as lines, one for each single factor, and historical GDP 
# data as open circles.
##
createSFLatticeGraph <- function(){
  dataTable <- loadData("All") #Grab the raw data
  predictionsK <- singleFactorPredictionsColumn("K") #Predictions from SF with K
  predictionsL <- singleFactorPredictionsColumn("L") #Predictions from SF with L
  predictionsQ <- singleFactorPredictionsColumn("Q") #Predictions from SF with Q
  predictionsX <- singleFactorPredictionsColumn("X") #Predictions from SF with X
  predictionsU <- singleFactorPredictionsColumn("U") #Predictions from SF with U
  #Now add the predictions columns to the data.
  dataTable <- cbind(dataTable, predictionsK, predictionsL, predictionsQ, predictionsX, predictionsU) 
  graphType <- "b" #b is for both line and symbol
  lineTypes <- c(0, 1, 2, 4, 1, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(0, 2, 1, 1, 1, 1) #line widths. 0 means no line.
  colors <- c("black", "black", "red", "blue", "darkorange", "darkgreen") #line and symbol colors
  symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
  graph <- xyplot(iGDP+predGDPK+predGDPL+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                  type=graphType,
                  index.cond=list(countryOrderForGraphs), #orders the panels.
                  layout=layoutSpec, #indicates a 3x3 arrangement of panels.
                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
                  pch = symbols, col.symbol = colors, #Controls symbol parameters
                  key=list(text=list(c("Actual", "With $k$", "With $l$", "With $q$", "With $x$", "With $u$")),
                           type=graphType,
                           cex=keyTextSize, #controls size of text in the key
                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
                           pch=symbols, col=colors, #controls symbol (plot characters) types
                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
                  scales=list(cex=scaleTextSize, #controls text size on scales.
                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                              y=list(relation="free", #allows each axis to be different
                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
                                     )
                              ), 
                  ylim=list(c(1,8), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3)),
                  xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
  return(graph)
}

# print(singleFactorPredictions("US", "K"))
# print(singleFactorPredictionsColumn("K"))
# print(singleFactorPredictionsColumn("L"))
# print(singleFactorPredictionsColumn("Q"))
# print(singleFactorPredictionsColumn("X"))
# print(singleFactorPredictionsColumn("U"))
# print(createSFLatticeGraph())

@@

<<SF_GDP_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.pos="H", fig.cap="Single-factor results.">>=
createSFLatticeGraph()
@

@@

<<cobb-douglas functions, eval=TRUE>>=
####################
# Returns an nls Cobb-Douglas model for the country specified
# Give an energyType ("Q", "X", or "U") if you want to include an energy term
##
cobbDouglasModel <- function(countryAbbrev, energyType){
  dataTable <- loadData(countryAbbrev) #Load the data that we need.
  #Run the non-linear least squares fit to the data based on whether we have an energy type or not.
  if (missing(energyType)){
    # No energy term desired in the Cobb-Douglas equation.
    # Establish guess values for alpha and lambda.
    lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
    alphaGuess <- 0.7 #0.7 gives good results for all countries.  
    # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
    modelCD <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha), 
                   data=dataTable, 
                   start = list(lambda=lambdaGuess, alpha=alphaGuess),
                   #Include the next 3 lines to fit with constraints.
                   #algorithm = "port",
                   #lower = list(lambda=-Inf, alpha=0), #constraints on lambda and alpha
                   #upper = list(lambda=Inf, alpha=1)
                   )
    return(modelCD)
  } else {
    # We need to do the Cobb-Douglas fit with the desired energy data.
    # To achieve the correct fit, we'll change the name of the desired column
    # to "iEToFit" and use "iEToFit" in the nls function. 
    dataTable <- replaceColName(dataTable, energyType, "iEToFit")
    # Reparameterize to ensure that we meet the constraints:
    # * alpha + beta + gamma = 1.0.
    # * alpha, beta, and gamma are all between 0.0 and 1.0.
    # To do this, we reparameterize as
    # * 0 < a < 1
    # * 0 < b < 1
    # * alpha = min(a, b)
    # * beta = b - a
    # * gamma = 1 - max(a, b)
    # Establish guess values for lambda, alpha, and beta.
    lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
    alphaGuess <- 0.9
    betaGuess <- 1.0 - alphaGuess
    aGuess <- alphaGuess
    bGuess <- alphaGuess + betaGuess
    # Now actually do the fit, using the column name "iEToFit".
    modelCDe <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEToFit^(1.0 - max(a,b)), 
                    data = dataTable,
                    start = list(lambda=lambdaGuess, a=aGuess, b=bGuess),
                    control = nls.control(maxiter = 200, 
                                          tol = 1e-05, 
                                          minFactor = 1/1024, 
                                          printEval=FALSE, #Tells whether to print details of curve fit process.
                                          warnOnly=TRUE),
                    #Include the next 3 lines to fit with constraints.
                    #algorithm = "port",
                    #lower = list(lambda=-Inf, a=0, b=0),
                    #upper = list(lambda= Inf, a=1, b=1)
                    )
    return(modelCDe)
  }
}

@@
